%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{RANJITH S}{ \urlstyle{same}\href{https://ranjiths.netlify.app/}{ranjiths.netlify.app} | {Software Developer}\\
\href{mailto:rsranjith2012@gmil.com}{rsranjith2012@gmail.com} | +91 9361217674 | \href{mailto:dd367@cornell.edu}{Leetcode Rating : 1000+}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Thiruvalluvar Univercity}
\descript{B.Sc in Chemistry}
\location{Tiruvannamalai, Tamilnanu}
\location{June 2022 | CGPA: 8.92 / 10}
\sectionsep

\subsection{GB HR SEC SCHOOL}
\descript{Maths Biolozy Top scorer}
\location{Melpallipattu , Tiruvannamalai}
\location{June 2019 | Cum per : 71.26}

\sectionsep

\subsection{govt high school }
\location{Andipatti , Tiruvannamalai}
\location{June 2017 | Cum per : 85.73 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Protfolio:// \href{https://ranjiths.netlify.app/}{\bf Ranjith } \\
Github:// \href{https://github.com/ranjith-sa}{\bf Ranjith-sa} \\
LinkedIn://  \href{https://www.linkedin.com/in/ranjith-sa/}{\bf Ranjith-sa} \\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Advanced:}
Python \textbullet{} JavaScript \textbullet{} React.Js  \textbullet{} Django  \\ \textbullet{} HTML  \textbullet{} CSS \textbullet{} Bootstrap \textbullet{} MySql \textbullet{} Jqurey \textbullet{} Git \& GitHub \\
\location{Intermediate:}
C \textbullet{} Node.js  \textbullet{} Flask \textbullet{} Pandas  \textbullet{} NumPy \textbullet{} Tkinter \textbullet{} Sqlite \\
\location{Familiar:}
C++ \textbullet{} Flutter  \textbullet{} NoSql \textbullet{} MongoDB
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}

Data Structures and Algorithms \\
Operating Systems \\
Data Science \\
Object Oriented Programming\\
Cloud Computing \\
Defending Computer Networks \\
Machine Learning \\
\sectionsep

\section{INTERESTS}
\subsection{TECHNICAL}
Robotics \textbullet{}  Block Chain \textbullet{} Full stack
Machine Learning \textbullet{} problem-solving  \\\
\subsection{NON - TECHNICAL}
Cricket\textbullet{}  Piano \textbullet{} Chess \textbullet{} Networking \textbullet{} Video Editing  \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ABOUT ME }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Experienced\textbf{ Python Full Stack Developer} with a strong background in Python, Django, MySQL, and \textbf{artificial intelligence}.
\item Passionate about shaping the electronics revolution with software solutions. 
\item Skilled in software development methodologies.
\item Proficient in implementing \textbf{algorithms} and \textbf{data structures}.
\item Strong collaborator in team environments.
\item Eager to apply expertise to \textbf{solve real-world problems} in the technology sector.
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECT'S
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{project}
\runsubsection{Protfolio }
\descript{ \href{https://ranjiths.netlify.app/}{\bf [ Live Link ]}  }
\descript{ Html | Css | Javascript | Git \& GitHub | Netlify }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Created a dynamic portfolio website using \textbf{HTML, CSS, and JavaScript}, showcasing \textbf{frontend development} skills.
\item Implemented version control and collaboration with \textbf{Git \& GitHub}.
\item Seamlessly hosted and deployed the website on \textbf{Netlify}, presenting projects and experiences with visual appeal and user-friendly navigation.
\end{tightemize}
\sectionsep

\runsubsection{Personal Finance Tracker}
\descript{ \href{https://github.com/ranjith-sa/E-Commerce-Website-in-Django/}{\bf [Live Link ]}  }
\descript{ Python | Django | React.js | SqLite3 | Javascript | RestAPI}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Integrated Django backend and React frontend for a seamless finance tracking experience.
\item Empowered users with features like \textbf{authentication, transaction} \textbf{management}, and \textbf{budget tracking}.
\item Streamlined data communication through \textbf{RESTful API} architecture for efficient performance and scalability.
\item Attracts \textbf{millions of daily users}, demonstrating widespread appeal and high traffic volume.



\end{tightemize}
\sectionsep



\runsubsection{E-Commerce }
\descript{ \href{https://github.com/ranjith-sa/E-Commerce-Website-in-Django/}{\bf [ GitHub Link ]}  }
\descript{ Python | Django | SqLite3 | Javascript | Html \& Css }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed an\textbf{ eCommerce} website utilizing HTML, CSS, Bootstrap, \textbf{Django}, and \textbf{Python}.
\item Integrated secure payment gateways and \textbf{user authentication} features using Django's robust capabilities.
\item Employed responsive design principles to ensure \textbf{cross-device compatibility} and seamless user experience.

\end{tightemize}
\sectionsep





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOFT SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SOFT SKILL}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Clear and concise \textbf{communication} fosters collaboration and understanding within teams.
\item  Resourcefulness in addressing challenges contributes to \textbf{efficient} project resolution and \textbf{innovation}.
\item  Organizing tasks and \textbf{prioritizing deadlines} ensures \textbf{timely delivery} of \textbf{quality work}.
\item  Collaborative spirit and cooperation promote synergy, leading to \textbf{successful project outcomes}.

\end{tightemize}




\end{minipage} 
\end{document}  \documentclass[]{article}
